---
title: "`geneName` Package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geneName)
library(data.table)
library(kableExtra)
```

## GitHub Documents

This package provides functions to convert human and mouse gene synonyms to gene names; and mouse gene names to human homologous genes.


## Examples

Here is an example data frame including gene names in one column:

```{r, echo=FALSE}
example<-fread("example.csv")
```

```{r, echo=FALSE}
knitr::kable(example, "simple")
```



`gnameconverter` function converts gene synonyms (if any) in the selected column to gene names. This makes it easier to transform gene synonyms to gene names even when the column contains a mixture of gene synonyms and gene names. This function can also be used to be sure all elements are gene names and there is no gene synonym in the table.
Output is the same data table with all other columns preserved.


## Usage

```{r, results='hide', message=FALSE}
df<-gnameConverter(example, "Gene name")
```

```{r, highlight=FALSE, echo=FALSE}
knitr::kable(df, "simple")
```



